MSB106 - Assignment

### 2023-02-14 MSB106_Assignment.qmd
Commit.

```{r, message=FALSE}
library(rgdal)
library(dplyr)
library(RSQLite)
library(sf)
library(tidyverse)
library(readr)
library(ggplot2)
library(kableExtra)
```

@@

>>>>

```{r, message=FALSE}
library(rgdal)
library(dplyr)
library(RSQLite)
library(sf)
library(tidyverse)
library(readr)
library(ggplot2)
library(kableExtra)
library(huxtable)
```

@@

```{r}
lm1 <- lm(Sum.salgsi ~ X_sum, data = Dentist_Data_LIMIT)
lm2 <- lm(Sum.salgsi ~ DistCBD + DistMal + X_sum, data = Dentist_Data_LIMIT)
```

```{r}
huxreg(list("Model 1" = lm1, "Model 2" = lm2), statistics = c(N = "nobs", R2 = "r.squared"), const. = "(Intercept)", note = "Note: {stars} T statistics in brackets.")
```
